---
title: "Journal"
author: "Lukas Buesch"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
options(knitr.duplicate.label = "allow")
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Intro to the tidyverse
In the following you will find my R Code and the corresponding plots for the challenge in the chapter **Intro to the tidyverse**.

#```{r <challenge 1>, cache=FALSE ,fig.width=10, fig.height=7}
#knitr::read_chunk('D:/SD(D)/BWL_data_science/ws20-business-data-science-basics---lab-journal-LukasBuesch/Intro_2_tidyverse/Bike_sales/sales_analysis#_challenge.R')
#```

```{r challenge_1, fig.width=14, fig.height=7}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS - Challenge ----

# 1.0 Load libraries ----
library(tidyverse)
library(readxl)
library(lubridate)


# 2.0 Importing Files ----

bikes_tbl      <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")


# 3.0 Joining Data ----

# leftjoin the specified columns to the orderlines_tbl

bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))


# 5.0 Wrangling Data ----

# Split the location column

bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  
  # 5.1 Separate location name
  
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  
  # 5.2 Add the total price (price * quantity) 
  # Add a column to a tibble that uses a formula-style calculation of other columns
  
  mutate(total.price = price * quantity) %>%
  
  # 5.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
  # 5.3.1 by exact column name
  
  select(-...1, -gender) %>%
  
  # 5.3.2 by a pattern
  
  select(-ends_with(".id")) %>%
  
  # 5.3.3 Actually we need the column "order.id". Let's bind it back to the data
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  # 5.3.4 You can reorder the data by selecting the columns in your desired order.
  
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  
  # 5.4 Rename columns -> dots to underscores
  
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

# 6.0 Business Insights ----
# 6.1 Sales by location (state) ----

# Step 1 - Manipulate

sales_by_location_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns
  
  select(state, total_price) %>%
  
  # Grouping by location and summarizing sales
  
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  
  # Optional: Add a column that turns the numbers into a currency format 
  # (makes it in the plot optically more appealing)
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

# Step 2 - Visualize

sales_by_location_tbl %>%
  
  # Setup canvas with the columns state (x-axis) and sales (y-axis)
  
  ggplot(aes(x = state, y = sales)) +
  
  # Geometries
  
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + # rotate x-labels
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    subtitle = "-",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )


# 6.2 Sales by Year and Category 2 ----

# Step 1 - Manipulate
sales_by_location_year_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and state
  
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

# Step 2 - Visualize
sales_by_location_year_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  #Trendline
  geom_smooth(method = "lm", se = FALSE) +
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and state",
    subtitle = "-",
    fill = "states" # Changes the legend name
  )


```


# Data Acquivision
In the following you will find my R Code and the corresponding plots for the challenges in the chapter **Data Acquivision**.

## Challenge 1 - API
For this challenge I decided to call a weather API, namely `OpenWeather`, to get the current weather in Hamburg.
```{r chapter_2_challenge_1}
# API challenge ----

# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.s
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(httr)


# 2.0 Get data  ----
# Get data from weather API  via function

weather_api <- function(city) {
  # path is city name
  API_key <- Sys.getenv("API_key")
  url <- modify_url(url = glue("https://api.openweathermap.org/data/2.5/weather?q={city}&appid={API_key}"))
  resp <- GET(url)
  stop_for_status(resp) # automatically throws an error if a request did not succeed
}


weather_hamburg_raw <- weather_api(city = "Hamburg")

weather_hamburg <- fromJSON(rawToChar(weather_hamburg_raw$content))

weather_hamburg


```


## Challenge 2 - Webscrapping