---
title: "Journal"
author: "Lukas Buesch"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
options(knitr.duplicate.label = "allow")
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Intro to the tidyverse
In the following you will find my R Code and the corresponding plots for the challenge in the chapter **Intro to the tidyverse**.

#```{r <challenge 1>, cache=FALSE ,fig.width=10, fig.height=7}
#knitr::read_chunk('D:/SD(D)/BWL_data_science/ws20-business-data-science-basics---lab-journal-LukasBuesch/Intro_2_tidyverse/Bike_sales/sales_analysis#_challenge.R')
#```

```{r challenge_1, fig.width=14, fig.height=7}
# Data Science at TUHH ------------------------------------------------------
# SALES ANALYSIS - Challenge ----

# 1.0 Load libraries ----
library(tidyverse)
library(readxl)
library(lubridate)


# 2.0 Importing Files ----

bikes_tbl      <- read_excel(path = "DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl  <- read_excel("DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")


# 3.0 Joining Data ----

# leftjoin the specified columns to the orderlines_tbl

bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))


# 5.0 Wrangling Data ----

# Split the location column

bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  
  # 5.1 Separate location name
  
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  
  # 5.2 Add the total price (price * quantity) 
  # Add a column to a tibble that uses a formula-style calculation of other columns
  
  mutate(total.price = price * quantity) %>%
  
  # 5.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
  # 5.3.1 by exact column name
  
  select(-...1, -gender) %>%
  
  # 5.3.2 by a pattern
  
  select(-ends_with(".id")) %>%
  
  # 5.3.3 Actually we need the column "order.id". Let's bind it back to the data
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  # 5.3.4 You can reorder the data by selecting the columns in your desired order.
  
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  
  # 5.4 Rename columns -> dots to underscores
  
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

# 6.0 Business Insights ----
# 6.1 Sales by location (state) ----

# Step 1 - Manipulate

sales_by_location_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns
  
  select(state, total_price) %>%
  
  # Grouping by location and summarizing sales
  
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  
  # Optional: Add a column that turns the numbers into a currency format 
  # (makes it in the plot optically more appealing)
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

# Step 2 - Visualize

sales_by_location_tbl %>%
  
  # Setup canvas with the columns state (x-axis) and sales (y-axis)
  
  ggplot(aes(x = state, y = sales)) +
  
  # Geometries
  
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + # rotate x-labels
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    subtitle = "-",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )


# 6.2 Sales by Year and Category 2 ----

# Step 1 - Manipulate
sales_by_location_year_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and state
  
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

# Step 2 - Visualize
sales_by_location_year_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  #Trendline
  geom_smooth(method = "lm", se = FALSE) +
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and state",
    subtitle = "-",
    fill = "states" # Changes the legend name
  )


```


# Data Acquivision
In the following you will find my R Code and the corresponding plots for the challenges in the chapter **Data Acquivision**.

## Challenge 1 - API
For this challenge I decided to call a weather API, namely `OpenWeather`, to get the current weather in Hamburg.
```{r chapter_2_challenge_1}
# API challenge ----

# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.s
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(httr)


# 2.0 Get data  ----
# Get data from weather API  via function

weather_api <- function(city) {
  # path is city name
  API_key <- Sys.getenv("API_key")
  url <- modify_url(url = glue("https://api.openweathermap.org/data/2.5/weather?q={city}&appid={API_key}"))
  resp <- GET(url)
  stop_for_status(resp) # automatically throws an error if a request did not succeed
}


weather_hamburg_raw <- weather_api(city = "Hamburg")

weather_hamburg <- fromJSON(rawToChar(weather_hamburg_raw$content))

weather_hamburg


```


## Challenge 2 - Webscrapping
I decided to analyze the website `https://www.rosebikes.de/`. Later I noticed that this Website uses sub categories for their bikes. I choosed the First search tree (mtb/trail-/-enduro/ground-control) for my analysis. The script saves the name (within the url) and the price.
```{r chapter_2_challenge_2}
# WEBSCRAPING ----

# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing
library(purrr)


# 1.1 COLLECT PRODUCT FAMILIES ----

url_home          <- "https://www.rosebikes.de/"

# Read in the HTML for the entire webpage
html_home         <- read_html(url_home)

# Web scrape the ids for the families
bike_family_tbl <- html_home %>%
  
  # Get the nodes for the families ...
  html_nodes(css = ".main-navigation-category-with-tiles__link") %>%
  # ...and extract the information of the id attribute
  html_attr("href") %>%
  
  # Remove the product families Gear and Outlet and Woman 
  # (because the female bikes are also listed with the others)
  discard(.p = ~stringr::str_detect(.x,"sale")) %>%
  
  # Convert vector to tibble
  enframe(name = "position", value = "family_class") %>%
  
  # Add a hashtag so we can get nodes of the categories by id (#)
  mutate(
    family_id = str_glue("#{family_class}")
  )

bike_family_tbl


# 1.2 COLLECT PRODUCT CATEGORIES ----

# Combine all Ids to one string to get all nodes at once
# (seperated by the OR operator ",")

family_id_css <- bike_family_tbl %>%
  
  pull(family_class) %>%
  
  stringr::str_c(collapse = ", ")


family_id_css



# 2.1 Get URL for each bike of the Product categories

# Create vector with all URLS for product classes

bike_category_url_tbl <- bike_family_tbl %>%
  
  # Convert vector to tibble
  select("position", "family_class") %>%
  
  # Add the domain, because we will get only the family_class
  mutate(
    url = glue("https://www.rosebikes.de{family_class}")
  ) %>%
  
  # delete multiple entries
  distinct(url)




# 2.1 Get URL for each bike of the Product categories

# select first bike category url
bike_category_url <- bike_category_url_tbl$url[1]

# Get the URLs for the bikes of the first category
html_bike_category  <- read_html(bike_category_url)
bike_sub_category_url_tbl        <- html_bike_category %>%
  
  # Get the 'a' nodes, which are hierarchally underneath 
  # the class productTile__contentWrapper
  html_nodes(css = ".catalog-category-bikes__picture-wrapper--left") %>%
  html_attr("href") %>%
  
  # Convert vector to tibble
  enframe(name = "position", value = "url") %>%

  # Add the domain, because we will get only the subdirectories

   mutate(url = glue("https://www.rosebikes.de{url}")) %>%
     
  # delete multiple entries
     
  distinct(url)


# search one Layer deeper

bike_sub_category_url <- bike_sub_category_url_tbl$url[1]

# Get the URLs for the bikes of the first subcategory

html_bike_sub_category  <- read_html(bike_sub_category_url)

bike_url_tbl        <- html_bike_sub_category %>%
  
  # Get the 'a' nodes, which are hierarchally underneath 
  # the class productTile__contentWrapper
  
  html_nodes(css = ".catalog-category-model__link") %>%
  html_attr("href") %>%
  
  # Convert vector to tibble
  
  enframe(name = "position", value = "url")



  # Add the full URL
  
bike_url_tbl$url <- paste("https://www.rosebikes.de", trimws(bike_url_tbl$url), sep = "")



  
  
# 2.1.2 Extract the descriptions (since we have retrieved the data already)
bike_url <- bike_url_tbl$url[1]
html_bike <- read_html(bike_url)

bike_desc_tbl <- html_bike %>%
  
  # Get the nodes in the meta tag where the attribute itemprop equals description
  html_nodes(".buybox__prize__wrapper > span") %>%
  
  # Extract the content of the attribute content
  html_attr("data-test") %>%
  
  # Convert vector to tibble
  enframe(name = "position", value = "price")





get_bike_data <- function(bike_url) {
  
  # Get the descriptions
  html_bike <- read_html(bike_url)
  bike_desc_tbl <- html_bike %>%
    html_nodes(".buybox__prize__wrapper > span") %>%
    html_attr("data-test") %>%
    enframe(name = "position", value = "price")
  
}





# Run the function with the first url to check if it is working
bike_url <- bike_url_tbl$url[1]
bike_data_tbl <- get_bike_data(bike_url)

bike_data_tbl



# 2.3.1a Map the function against all urls

# Extract the urls as a character vector
bike_url_vec <- bike_url_tbl %>% 
  pull(url)

# Run the function with every url as an argument
bike_data_lst <- map(bike_url_vec, get_bike_data)

# Merge the list into a tibble
bike_data_tbl <- bind_rows(bike_data_lst)


name_with_price = bind_cols(bike_data_tbl,bike_url_tbl$url)

name_with_price





```